# Python

```{r setup3, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, include=FALSE}
workingDir <-  "."
setwd(workingDir)
```


## A normal R code chunk

```{r}
library(reticulate)
x = 42
print(x)
```

## Modify an R variable

In the following chunk, the value of `x` on the right hand side
is `r x`, which was defined in the previous chunk.

```{r}
x = x + 12
print(x)
```

## A Python chunk

This works fine and as expected. 

```{python}
x = 42 * 2
print(x) 
```

The value of `x` in the Python session is `r py$x`.
It is not the same `x` as the one in R.

## Modify a Python variable

```{python}
x = x + 18 
print(x)
```

Retrieve the value of `x` from the Python session again:

```{r}
py$x
```

Assign to a variable in the Python session from R:

```{r}
py$y = 1:5
```

See the value of `y` in the Python session:

```{python}
print(y)
```

## Python graphics

You can draw plots using the **matplotlib** package in Python.

```{python}
import matplotlib.pyplot as plt
plt.plot([0, 2, 1, 4])
plt.show()
```

## Tipos de datos

```{python}
x = 'hello, python world!'
print(x.split(' '))
```

## Flujo de control

## Visualizaci칩n de datos

## Manipulaci칩n de bases de datos

## An치lisis exploratorio de bases de datos

## Funciones y scripts

## Buenas practicas

## Procesamiento de alto rendimiento

## Programaci칩n en paralelo